Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-28 main_paper.tex
Rename appendix
More very small changes related to the kernel description

\title{Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
  with Uniform Kernels}

@@

Assumption~\ref{A2} specifies the bandwidth conditions assumed by CCT, which we
will also use in this paper.
\begin{assumption}[Bandwidth]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.} %
  The relationship $h_{n} \leq b_{n}$ also holds for all $n$.
\end{assumption}

In the next section, we build upon the insight provided by CCT bias-corrected
estimator and propose a simple bootstrap procedure that can directly construct
the robust CIs without requiring the derivation of analytical formulas and
direct estimators for the bias, variance and covariance terms, while relying on
the same first-order bias correction approximation. The requirement $h < b$ is
new to this paper, because the bootstrap can not be implemented for the uniform
kernel without it, but the other parts of Assumption~\ref{A2} are taken from
CCT.

@@

\section{Proofs of mathematical results}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau_h - \Delta^*_h - \tau = (\hat\tau_h - \E \hat \tau_h) +
  (\E \hat \tau_h - \tau) - (\E^* \hat \tau^*_h - \tau^*)
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \label{eq:6}
  \E^* \hat\mu_{+}^*(h_n) - \mu_{+}^{*}
  &= h_n^{2} \mu_+^{*(2)} \Bf_{+}(h_n)/2,
  &\E^* \hat\mu_{-}^*(h_n) - \mu_{-}^{*}
  &= h_n^{2} \mu_-^{*(2)} \Bf_{-}(h_n)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
  \label{eq:7}
    \E^* \hat\tau^{*}_h - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2 \notag \\
  \label{eq:8}
  &\pushright{- h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b_n)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b_n)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
$\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

>>>>

\title{Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
  with the Uniform Kernel}

@@

Assumption~\ref{A2} specifies the bandwidth conditions assumed by CCT, which we
will also use in this paper.
\begin{assumption}[Bandwidth]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.} %
  The relationship $h \leq b$ also holds for all $n$.
\end{assumption}

In the next section, we build upon the insight provided by CCT bias-corrected
estimator and propose a simple bootstrap procedure that can directly construct
the robust CIs without requiring the derivation of analytical formulas and
direct estimators for the bias, variance and covariance terms, while relying on
the same first-order bias correction approximation. The requirement $h < b$ is
new to this paper, because the bootstrap can not be implemented for the uniform
kernel without it, but the other parts of Assumption~\ref{A2} are taken from
CCT.\footnote{%
  This assumption can be relaxed by considering other kernels, which is the
  subject of current research by the authors.} %

@@

\appendix
\section{Mathematical appendix}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau_h - \Delta^*_h - \tau = (\hat\tau_h - \E \hat \tau_h) +
  (\E \hat \tau_h - \tau) - (\E^* \hat \tau^*_h - \tau^*)
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \label{eq:6}
  \E^* \hat\mu_{+}^*(h_n) - \mu_{+}^{*}
  &= h_n^{2} \mu_+^{*(2)} \Bf_{+}(h_n)/2,
  &\E^* \hat\mu_{-}^*(h_n) - \mu_{-}^{*}
  &= h_n^{2} \mu_-^{*(2)} \Bf_{-}(h_n)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
  \label{eq:7}
    \E^* \hat\tau^{*}_h - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2 \notag \\
  \label{eq:8}
  &\pushright{- h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b_n)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b_n)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
$\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed
